### 2015-05-23 docs/report/array_merging.tex
Finished initial corrections pass

\subsection{\ttarray{} merge benchmark}
Unlike the case for \ttarray{} splitting (\ref{subsec:copying-typed-arrays}) there aren't that many native alternatives to create a \ttarray{} from smaller ones.

@@

For illustrative purposes, a naive implementation (without optimizations or error checking) would be similar to the following one:
\begin{lstlisting}[caption=Simple \ttarray{} merge function]
function merge(arrays){
  var first = arrays[0];
  var total = arrays.reduce(function(c,a) { return c + a.length; }, 0);
  var result = new first.constructor(total);
  var start = 0;

>>>>

\subsection{\ttarray{} merge benchmark}
Unlike the case for \ttarray{} splitting (Section~\ref{subsec:copying-typed-arrays}) there aren't that many native alternatives to create a \ttarray{} from smaller ones.

@@

For illustration purposes, a naive implementation (without optimizations or error checking) would be similar to the following one:
\begin{lstlisting}[caption=Simple \ttarray{} merge function]
function merge(arrays){
  var first = arrays[0];
  var total = arrays.reduce(function(c,a) { return c + a.length; }, 0);
  var result = new first.constructor(total);
  var start = 0;
